A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration

### 2020-08-21 paper/aimusic2020/paper.tex
minor modif for submission

% first the title is needed
\title{Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Carmine Emanuele Cella\inst{1}\and Luke Dzwonczyk\inst{1}\and Alejandro Saldarriaga-Fuertes\inst{1}\and Hongfu Liu\inst{2}\and Helene-Camille Crayencour\inst{3}}
%
% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
\authorrunning{Carmine Emanuele Cella et al.}

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{University of California, Berkeley \and InstituteB\\ \email{ , dz.luke@berkeley.edu, }}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.17]{../latex/figs/method.png}
	\caption{An overview of the proposed method for assisted orchestration with neural models. Instruments and pitches are determined as peaks of the output probability distribution, while the dynamics are computed by quantizing the probabilities. \label{fig:method}}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{.65\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{../latex/figs/Acc_vs_N_CNN.png}
  \caption{CNN with LSTM}
  \label{best_acc_cnn}
\end{subfigure}%
\begin{subfigure}{.65\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{../latex/figs/Acc_vs_N_ResNet.png}
  \caption{ResNet}
  \label{best_acc_resnet}
\end{subfigure}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM and the ResNet depending on the number of instruments in the combinations}
\end{figure}

@@

\begin{table*}
  \centering
     \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \ref{distance} was used to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}\label{orch_eval}
	\centering    
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}

\end{table*}

>>>>

% first the title is needed
\title{A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Carmine Emanuele Cella\inst{1}\and Luke Dzwonczyk\inst{1}\and Alejandro Saldarriaga-Fuertes\inst{1}\and Hongfu Liu\inst{1}\and Helene-Camille Crayencour\inst{2}}
%
% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
\authorrunning{Carmine Emanuele Cella et al.}

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{University of California, Berkeley \and Centrale Sup\'elec, L2S, Univ. Paris-Saclay, CNRS \\ \email{carmine.cella@berkeley.edu, dz.luke@berkeley.edu }}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.20]{../latex/figs/method.png}
	\caption{An overview of the proposed method for assisted orchestration with neural models. Instruments and pitches are determined as peaks of the output probability distribution, while the dynamics are computed by quantizing the probabilities. \label{fig:method}}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{.52\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{../latex/figs/Acc_vs_N_CNN.png}
  \caption{CNN with LSTM}
  \label{best_acc_cnn}
\end{subfigure}%
\begin{subfigure}{.52\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{../latex/figs/Acc_vs_N_ResNet.png}
  \caption{ResNet}
  \label{best_acc_resnet}
\end{subfigure}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM and the ResNet depending on the number of instruments in the combinations}
\end{figure}

@@

\begin{table*}
	\centering    
  \resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}}
    \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \ref{distance} was used to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}\label{orch_eval}
\end{table*}
